\cleardoublepage
%\pagebreak
\phantomsection
\addcontentsline{toc}{chapter}{Acknowledgements}
\chapter*{Acknowledgments}
\vspace{1.0in}
If all goes as planned, this might be my last chance to write an acknowledgment in a research report. As a child, I always dreamed of becoming a scientist, conducting research, publishing papers, and, just like many renowned scholars, writing a list of names that hold great significance to me in the preface or acknowledgment of a paper or monograph.

It might seem a bit out of place, but I want to say sorry to the little girl I was 10 years ago. You didn't end up becoming a scientist as you dreamed; instead, you ventured into the world of finance—something you had never imagined. But this is not a story of unfulfilled ambitions; rather, it’s the best outcome of a journey full of deliberate choices and explorations. I am grateful for all the classmates, teachers, and friends I’ve met during these four years in France. The world of finance also has its fascinating challenges, talented individuals, ever-evolving technologies, and, along with that, a reward that allows another dream of yours—to taste food from around the world—to come true.

Societe Generale (SG) has played a crucial role in my journey. I would like to express my deepest gratitude to my two mentors during this research internship, Ismail and Sebastian, for their trust, support, and guidance throughout this experience. Their exceptional personalities have provided me with role models to look up to. Ismail is always brimming with curiosity and enthusiasm, and I can truly sense his passion for this industry. Meanwhile, Sebastian has an incredible ability to articulate complex problems with the precision of a surgeon's scalpel, teaching me many "unquantifiable" lessons. Additionally, every colleague and fellow intern in the team has made this journey both rewarding and enjoyable.

I also want to thank my parents. Although they may not understand the English or French I use daily, they have always been my strongest support. Lastly, I want to thank my friends; there’s an even broader horizon ahead in life.


